Making multiple-locus association mapping on a genome-wide scale routine

### 2017-11-06 AM+draft.tex
07 Nov, 2017

gemma

>>>>

\textbf{FaST-LMM:}  FaST-LMM is a highly efficient stand along computer program for association mapping. It is based on a standard single-locus model (refs). Its computational efficiencies come through rotating the data with spectral decomposition. This 
transforms the linear mixed 
model into a much simpler linear model.  In doing so, FaST-LMM inherits the favourable property of having its analyses 
scale linearly, in both run time and memory, with sample size ($n$).

\textbf{gemma}
